Community engagement and subgroup meta-knowledge: Some factors in the soul of a community

### 2018-12-28 PaperFinalDraft.Rnw
change affiliation
update reference to editorial
mention reproducibility and add citation

\author{Amelia McNamara}
\institute{A. McNamara \at
              8125 Math Sciences Bldg. \\
              Los Angeles, CA 90095-1554 \\
              \email{amelia.mcnamara@stat.ucla.edu}
}

@@

This article is one of several related to the Knight Foundation community data from the 2013 Data Expo. For more information on the Expo and the data sets, see \citep{HofWic20XX}.

>>>>

\author{Amelia McNamara}
\institute{A. McNamara \at
              Burton 215 \\
              Smith College
              Northampton, MA 01063 \\
              \email{amcnamara@smith.edu}
}

@@

This article is one of several related to the Knight Foundation community data from the 2013 American Statistical Association Data Expo. For more information on the Expo and the data sets, see \citep{Hof2019}. This article is fully-reproducble, with all code necessary to generate the paper available on GitHub~\citep{McN2019}. In the GitHub repository, you will find the underlying data, the LaTeX/knitr file which produces the paper including R code, a packrat archive of the necessary R packages, and LaTeX style files to create the specific journal style.
